Community engagement and subgroup meta-knowledge: Some factors in the soul of a community

### 2018-12-31 PaperFinalDraft.Rnw
added sample sizes to faceted plots

minGroups09 <- LikertData(positive, negative, neutral, minoritiesYN09)
minGroups09$neg$Response <- factor(minGroups09$neg$Response, levels=levels(minGroups09$neg$Response)[c(2,3,1)])
@

<<allMinorities,out.width="0.99\\linewidth",fig.width = 10.5, fig.height=12.5, fig.cap="Responses to the question, \`\`How is your community as a place for racial and ethnic minorities?\" faceted by community (2009 data)." >>=
baseplot <- ggplot(mapping = aes(InGroup, Freq, fill = Response, order=Response)) + 
  facet_wrap(~citystate, ncol=3) + 
  geom_bar(data = minGroups09$neg, stat = "identity") + 
  geom_bar(data = minGroups09$pos, stat = "identity") + 
  scale_fill_manual(
    values=colorsA, 
    breaks=c("Very bad", "2", "3", "4", "Very good"),
    name="Response"
    ) + 
  coord_flip() +
#TRUE means minorities, in Aberdeen they are under-rating
  scale_y_continuous(
    breaks=seq(from=-0.25, to=0.75, by=0.25), 
    labels=percent
    ) + 
  scale_x_discrete(labels=c("White", "Non-white")) + 
  xlab("") + 
  ylab("") + 
  theme(
    legend.text=element_text(size=14), 
    legend.title=element_text(size=16), 
    axis.text.y=element_text(size=16), 
    title=element_text(size=16), 
    axis.text.x=element_text(size=14), 
    strip.text=element_text(size=14))

@@

<<seniorPlot, out.width="0.99\\linewidth",fig.width = 10.5, fig.height=12.5, fig.cap="Responses to the question, \`\`How is your community as a place for seniors?\" faceted by community (2009 data). Every community follows the pattern of over-rating by seniors, but some communities have a smaller discrepancy between ratings of seniors and non-seniors.">>=
baseplot <- ggplot(mapping = aes(InGroup, Freq, fill = Response, order = Response)) + 
  facet_wrap(~citystate, ncol=3) + 
  geom_bar(data = seniorGroup09$neg, stat = "identity") + 
  geom_bar(data = seniorGroup09$pos, stat = "identity") + 
  scale_fill_manual(
    breaks=c("Very bad", "2", "3", "4", "Very good"), 
    values=colorsA, 
    name="Response"
    ) + 
  coord_flip() + 
  scale_y_continuous(
    breaks=seq(from=-0.25, to=0.75, by=0.25), 
    labels=percent
    ) + 
  scale_x_discrete(labels=c("Non-seniors", "Seniors")) + 
  xlab("") + 
  ylab("") + 
  theme(
    legend.text=element_text(size=14), 
    legend.title=element_text(size=16), 
    axis.text.y=element_text(size=16), 
    title=element_text(size=16), 
    axis.text.x=element_text(size=12),
    strip.text=element_text(size=14))

@@

<<kidPlot, out.width="0.99\\linewidth",fig.width = 10.5, fig.height=12.5, fig.cap="Responses to the question, \`\`How is your community as a place for families with young children?\" faceted by community (2009 data). Interestingly, most communities follow the pattern of similar ratings by both groups, but there is a lot of variation between communities in terms of the overall rating.">>=
baseplot <- ggplot(mapping = aes(InGroup, Freq, fill = Response, order=Response)) + 
  facet_wrap(~citystate, ncol=3) + 
  geom_bar(data = kidGroups$neg, stat = "identity") + 
  geom_bar(data = kidGroups$pos, stat = "identity") + 
  scale_fill_manual(
    breaks=c("Very bad", "2", "3", "4", "Very good"), 
    values=colorsA, 
    name="Response"
    ) + 
  coord_flip() + 
  scale_y_continuous(
    breaks=seq(from=-0.25, to=0.75, by=0.25), 
    labels=percent
    ) + 
  scale_x_discrete(labels=c("Childless \n households", "Families \n with children")) + 
  xlab(" ") + 
  ylab("") + 
  theme(
    legend.text=element_text(size=14), 
    legend.title=element_text(size=16), 
    axis.text.y=element_text(size=16), 
    title=element_text(size=16), 
    axis.text.x=element_text(size=10))

>>>>

minGroups09 <- LikertData(positive, negative, neutral, minoritiesYN09)
minGroups09$neg$Response <- factor(minGroups09$neg$Response, levels=levels(minGroups09$neg$Response)[c(2,3,1)])

totalMin09 <- minoritiesYN09 %>%
  group_by(citystate, InGroup) %>%
  summarize(totalN = sum(n))
@

<<allMinorities,out.width="0.99\\linewidth",fig.width = 10.5, fig.height=12.5, fig.cap="Responses to the question, \`\`How is your community as a place for racial and ethnic minorities?\" faceted by community (2009 data). Numbers in parentheses indicate sample sizes." >>=
baseplot <- ggplot() + 
  facet_wrap(~citystate, ncol=3) + 
  geom_bar(mapping = aes(InGroup, Freq, fill = Response, order=Response), data = minGroups09$neg, stat = "identity") + 
  geom_bar(mapping = aes(InGroup, Freq, fill = Response, order=Response), data = minGroups09$pos, stat = "identity") + 
  scale_fill_manual(
    values=colorsA, 
    breaks=c("Very bad", "2", "3", "4", "Very good"),
    name="Response"
    ) + 
  coord_flip() +
#TRUE means minorities, in Aberdeen they are under-rating
  scale_y_continuous(
    breaks=seq(from=-0.5, to=0.75, by=0.25), 
    labels=percent
    ) + 
  scale_x_discrete(labels=c("White", "Non-white")) + 
  xlab("") + 
  ylab("") + 
  theme(
    legend.text=element_text(size=14), 
    legend.title=element_text(size=16), 
    axis.text.y=element_text(size=16), 
    title=element_text(size=16), 
    axis.text.x=element_text(size=11), 
    strip.text=element_text(size=14)) +
  geom_text(data=totalMin09, aes(label=paste0("(",totalN, ")"), x=InGroup, y=1.1), size=3, hjust=1) +
  expand_limits(y=1)

@@

<<seniorPlot, out.width="0.99\\linewidth",fig.width = 10.5, fig.height=12.5, fig.cap="Responses to the question, \`\`How is your community as a place for seniors?\" faceted by community (2009 data). Numbers in parentheses are sample sizes. Every community follows the pattern of over-rating by seniors, but some communities have a smaller discrepancy between ratings of seniors and non-seniors.">>=

totalSeniors09 <- seniorYears %>%
  ungroup() %>%
  filter(year==2009) %>%
  group_by(citystate, InGroup) %>%
  summarize(totalN = sum(n))

baseplot <- ggplot() + 
  facet_wrap(~citystate, ncol=3) + 
  geom_bar(mapping = aes(InGroup, Freq, fill = Response, order = Response), data = seniorGroup09$neg, stat = "identity") + 
  geom_bar(mapping = aes(InGroup, Freq, fill = Response, order = Response), data = seniorGroup09$pos, stat = "identity") + 
  scale_fill_manual(
    breaks=c("Very bad", "2", "3", "4", "Very good"), 
    values=colorsA, 
    name="Response"
    ) + 
  coord_flip() + 
  scale_y_continuous(
    breaks=seq(from=-0.25, to=0.75, by=0.25), 
    labels=percent
    ) + 
  scale_x_discrete(labels=c("Non-seniors", "Seniors")) + 
  xlab("") + 
  ylab("") + 
  theme(
    legend.text=element_text(size=14), 
    legend.title=element_text(size=16), 
    axis.text.y=element_text(size=16), 
    title=element_text(size=16), 
    axis.text.x=element_text(size=12),
    strip.text=element_text(size=14)) +
  geom_text(data=totalSeniors09, aes(label=paste0("(",totalN, ")"), x=InGroup, y=1.1), size=3, hjust=1) +
  expand_limits(y=1)

@@

<<kidPlot, out.width="0.99\\linewidth",fig.width = 10.5, fig.height=12.5, fig.cap="Responses to the question, \`\`How is your community as a place for families with young children?\" faceted by community (2009 data). Interestingly, most communities follow the pattern of similar ratings by both groups, but there is a lot of variation between communities in terms of the overall rating.">>=
totalkids09 <- kidGroup09 %>%
  ungroup() %>%
  group_by(citystate, InGroup) %>%
  summarize(totalN = sum(n))

baseplot <- ggplot() + 
  facet_wrap(~citystate, ncol=3) + 
  geom_bar(mapping = aes(InGroup, Freq, fill = Response, order=Response), data = kidGroups$neg, stat = "identity") + 
  geom_bar(mapping = aes(InGroup, Freq, fill = Response, order=Response), data = kidGroups$pos, stat = "identity") + 
  scale_fill_manual(
    breaks=c("Very bad", "2", "3", "4", "Very good"), 
    values=colorsA, 
    name="Response"
    ) + 
  coord_flip() + 
  scale_y_continuous(
    breaks=seq(from=-0.25, to=0.75, by=0.25), 
    labels=percent
    ) + 
  scale_x_discrete(labels=c("Childless \n households", "Families \n with children")) + 
  xlab(" ") + 
  ylab("") + 
  theme(
    legend.text=element_text(size=14), 
    legend.title=element_text(size=16), 
    axis.text.y=element_text(size=16), 
    title=element_text(size=16), 
    axis.text.x=element_text(size=10)) +
  geom_text(data=totalkids09, aes(label=paste0("(",totalN, ")"), x=InGroup, y=1.2), size=3, hjust=1) +
  expand_limits(y=1)
